Tree regeneration in models of forest dynamics: a key priority for further research

### 2023-04-26 manuscript/manuscriptRW.Rmd
changes in table 1 to remove the model classification

#footnotes
names(modelDF)[2] <- paste0(names(modelDF)[2], "(a)")
names(modelDF)[3] <- paste0(names(modelDF)[3], "(b)")
names(modelDF)[4] <- paste0(names(modelDF)[4], "(c)")
names(modelDF)[5] <- paste0(names(modelDF)[5], "(d)")
names(modelDF)[6] <- paste0(names(modelDF)[6], "(e)")
names(modelDF)[11] <- paste0(names(modelDF)[11],"(f)")

kable(modelDF,
      format = "latex", booktabs = TRUE,
      caption = "Models included and their characteristics.") |>
        kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down") |>
    # fix width by column
      kableExtra::column_spec(column = 1, width = "5em") |>
      kableExtra::column_spec(column = 2, width = "3em") |>
      kableExtra::column_spec(column = 3, width = "3em") |>
      kableExtra::column_spec(column = 4, width = "4em") |>
      kableExtra::column_spec(column = 5, width = "5em") |>
      kableExtra::column_spec(column = 6, width = "5em") |>
      kableExtra::column_spec(column = 7, width = "5em") |>
      kableExtra::column_spec(column = 8, width = "8em") |>
      kableExtra::column_spec(column = 9, width = "8em") |>
      kableExtra::column_spec(column = 10, width = "5em") |>
      kableExtra::column_spec(column = 11, width = "5em") |>
      kableExtra::column_spec(column = 12, width = "8em") |>
      kableExtra::add_footnote(c("S-Stand, L-Landscape, G-Global",
                                 "PB-Process based, EM-Empirical",
                                 "C-Cohort, I-Individual",
                                 "RG-Regeneration, RC-Recruitment",
                                 "Y-Yes, N-No",
                                 "D-Daily, M-Monthly"),

>>>>

#footnotes
names(modelDF)[2] <- paste0(names(modelDF)[2], "(a)")
names(modelDF)[3] <- paste0(names(modelDF)[3], "(b)")
names(modelDF)[4] <- paste0(names(modelDF)[4], "(c)")
names(modelDF)[6] <- paste0(names(modelDF)[6], "(d)")
names(modelDF)[11] <- paste0(names(modelDF)[11],"(e)")

kable(modelDF,
      format = "latex", booktabs = TRUE,
      caption = "Models included and their characteristics.") |>
        kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down") |>
    # fix width by column
      kableExtra::column_spec(column = 1, width = "5em") |>
      kableExtra::column_spec(column = 2, width = "3em") |>
      kableExtra::column_spec(column = 3, width = "4em") |>
      kableExtra::column_spec(column = 4, width = "5em") |>
      kableExtra::column_spec(column = 5, width = "5em") |>
      kableExtra::column_spec(column = 6, width = "5em") |>
      kableExtra::column_spec(column = 7, width = "8em") |>
      kableExtra::column_spec(column = 8, width = "8em") |>
      kableExtra::column_spec(column = 9, width = "5em") |>
      kableExtra::column_spec(column = 10, width = "5em") |>
      kableExtra::column_spec(column = 11, width = "8em") |>
      kableExtra::add_footnote(c("S-Stand, L-Landscape, G-Global",
                                 "PB-Process based, EM-Empirical",
                                 "C-Cohort, I-Individual",
                                 "Y-Yes, N-No",
                                 "D-Daily, M-Monthly"),
